---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# brapiui

The goal of brapiui is to faciliate functions for interactive exploration of data from the Breeding API. This integrates with RStudio.  Also, to provide re-usable widgets for shiny applications as well as full local shiny based interface to the breeding API.

# Note

As of February 2018 only one small function is implemented.

## Installation

You can install brapiui from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("c5sire/brapiui")
```

## Example

Note: You also need to install the brapi package.

```{r brapi-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("CIP-RIU/brapiui")
```


This is a basic example which shows you how to solve a common problem:

```{r example, eval=FALSE}
## basic example code

con <- brapi::ba_db()$sweetpotatobase
loc <- brapi::ba_locations(con, pageSize = 100)
brapiui::bu_map(loc)

```
